The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-18 EducProposal.Rmd
Re-arranged and tried to simplify code chunks in proposal

# Install necessary packages
# Install rempis from Christpher Gandrud's website
devtools::install_github('christophergandrud/repmis')
library(repmis)
# Load citation package
pkgs <- c('dplyr','ggplot2')
repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')

@@

Our main hypothesis would be that the more culturally group-oriented and the more self-confident a population is, the higher should entrepreneurship in that country be.

Aside the sense of belonging as defined by OECD PISA study, here are some of the items from the World Value Survey 2005-2009 wave I could use to build the indexes about “sense of belonging to a group“, “sense of individuality” and “degree of self confidence”.

###Concepts that I may need for my research

####Return on Investment
Self-confidence: It is difficult to obtain a credible measurement of self confidence, how should I measure this?

Positive reinforcement is more easily defined but is also culture-dependent. Individual-focused systems vs group-oriented ones, how do you delimitate?

Types of management

Return on Investment, how do you evaluate euros of tomorrow or value for money rate, perhaps using the social discount rate for some part, but also considering the potential GDP that could result from another education system management and culture vs what you would get carrying on like now.

>>>>

# Install necessary packages
# Install rempis from Christpher Gandrud's website
devtools::install_github('christophergandrud/repmis')
library(repmis)
# Load citation package
pkgs <- c('dplyr','ggplot2','repmis')
repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')

@@

Our main hypothesis is that the more culturally group-oriented and the more self-confident a population is, the higher entrepreneurship in that country will be.

###Neccesary Concepts  
1. Return on Investment: Assigning a future Euro value to a present-day investment. This may require the use of a social deiscout rate, but will also need to consider the potential GDP increase brought about by improved education policies.

2. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but the study considers how this increased self-confidence positively affects GDP and the rate of entrepeurship in a given country. It will therefore need to include some quantiative approach to measuring this factor.

3. Positive reinforcement: This is easier to define than self-confience, but it is also culture-dependent (individual-focused systems vs group-oriented ones). This will also need to be quantified for the qualitative portion of this project.

4. Types of management: This study focuses on social issues and how these factors affect entrepreneurship, but management styles can transcend social norms. Control variables will need to be identified to address this.
